\section{Contributions}
The contributions section is not included in the 6 page limit. This section should describe what each team member worked on and contributed to the project.

Joren Mangelschots: I worked on the neural network methods. I started by using the code of the exercise session about "neural networks for multiclass classification". I used the .csv file provided by the dataset from which I get the image path, then I transform the image to an array which i store in my X variable, as my Y I store the labels of the corresponding species of birds. I first used the model of the exercise session which adapted so the output layer contains 50 neurons and the first two connected layers contain 64 neurons. I added a flatten layer before the connected layers to have a 1D array to insert in my connected layers. 

To improve the changed model I increased the amount of layers and the amount of neurons to increase the complexity of the model. This way I would have more trainable parameters. Then i compared both of these models. I changed the learning rate to find the best value for me and also played around with some batch sizes. The learning rate for the end result is 0.001 for both models, and the batch size is 32 for both. With these values I got the best result. I kept the improved model only with more layers and neurons and without any dropout layers or other techniques to prevent overfitting. To really be able to display the result of adding more layers and more neurons to your model. 